Topology and experimental distinguishability

### 2018-02-13 Articles/TopologyAndExperimentalDistinguishability/article-topologyproceedings.tex
Version of the article submitted to topology proceedings

\documentclass[preprint]{elsarticle}

% Temporary to remove "submitted to"
\makeatletter
\def\ps@pprintTitle{%
	\let\@oddhead\@empty
	\let\@evenhead\@empty
	\def\@oddfoot{}%
	\let\@evenfoot\@oddfoot}
\makeatother

\usepackage{lineno,hyperref}

\usepackage{amsmath, amsthm, amsfonts}
\usepackage[only,llbracket, rrbracket,llparenthesis,rrparenthesis]{stmaryrd}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}

\theoremstyle{plain}% default 
\newtheorem{thm}{Theorem}[section] 
\newtheorem{lem}[thm]{Lemma} 
\newtheorem{prop}[thm]{Proposition} 
\newtheorem{cor}[thm]{Corollary}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
%\newtheorem{exmp}{Example}[section]
\theoremstyle{remark}
\newtheorem*{rem}{Remark}
\modulolinenumbers[5]

\journal{Topology and its Applications}

@@

\begin{frontmatter}

@@

%% Group authors per affiliation:

\author[]{Christine A. Aidala}
\ead{caidala@umich.edu}

\author[]{Gabriele Carcassi\corref{cor1}}
\ead{carcassi@umich.edu}

\author[]{Mark J. Greenfield}
\ead{markjg@umich.edu}

\address{University of Michigan, Ann Arbor, MI 48109, USA}

\cortext[cor1]{Corresponding author}

@@

\begin{keyword}
topological spaces \sep scientific foundations \sep function space
\MSC[2010] 54H99 \sep 00A79
\end{keyword}

\end{frontmatter}

%\linenumbers

\section{Introduction}

@@

\section{Experimental observations}

@@

\section{Algebra of experimental observations}

@@

\section{Experimental domain}

@@

\section{Experimental distinguishability}

@@

\section{Experimental relationships}

@@

\section{Distinguishability of experimental relationships}

@@

\begin{table}[h]
	\centering
	\begin{tabular}{p{0.20\textwidth} p{0.7\textwidth}}
		Math/Topology & Science/Physics \\ 
		\hline 
		Hausdorff, second-countable space & Space of experimentally distinguishable elements, whose points are the possible values and whose open sets represent the experimentally attainable levels of precision. \\
		Open set & Verifiable set. We can verify experimentally that an element is within the set.  \\ 
		Closed set & Refutable set. We can verify experimentally that an element is not in the set. \\ 
		Basis & A collection of verifiable sets that can be used to distinguish an element\\
		Continuous \newline function &  An experimental relationship between two sets of experimentally distinguishable elements, which must preserve distinguishability \\
		Homeomorphism &  A perfect equivalence between spaces of experimentally distinguishable elements. \\
	\end{tabular} 
	\caption{Topology-to-physics dictionary. This table sums up the relationships established between mathematical and scientific concepts.}
\end{table}

\section{Conclusion}

@@

\section*{Acknowledgments}
Funding for this work was provided in part by the MCubed program of the University of Michigan.

\bibliographystyle{elsarticle-num}
\bibliography{bibliography}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%           Topology Proceedings Sample Latex Article             %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{amsart}
\usepackage[T1]{fontenc}   %%%%%%%Please do not change
%\usepackage{graphics}                  %%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Please do not change this paragraph. %%%%%%%
\setcounter{page}{1}                   %%%%%%%
\setlength{\textwidth}{4.4in}          %%%%%%%
\setlength{\textheight}{7.0in}         %%%%%%%
\setlength{\evensidemargin}{1in}       %%%%%%%
\setlength{\oddsidemargin}{1in}        %%%%%%%
\setlength{\topmargin}{.8in}           %%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Please do not change the page size   %%%%%%%
% and do not redefine the baselineskip.%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}

\newtheorem{rem}[thm]{Remark}
\numberwithin{equation}{section}

\usepackage{amsmath, amsthm, amsfonts, float}
\usepackage[only,llbracket, rrbracket,llparenthesis,rrparenthesis]{stmaryrd}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This a placeholder for the TOPLOGY PROCEEDINGS logo %%%%%%
\noindent                                             %%%%%%
\begin{picture}(150,36)                               %%%%%%
\put(5,20){\tiny{Submitted to}}                       %%%%%%
\put(5,7){\textbf{Topology Proceedings}}              %%%%%%
\put(0,0){\framebox(140,34){}}                        %%%%%%
\put(2,2){\framebox(136,30){}}                        %%%%%%
\end{picture}                                        %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.5in}

\renewcommand{\bf}{\bfseries}
\renewcommand{\sc}{\scshape}
%insert defs/styles
\vspace{0.5in}

@@

%    Information for first author:
\author{Christine A. Aidala}
\address{Department of Physics; University of Michigan; Ann Arbor, MI 48109}
%    Current address (if needed):
%\curraddr{}
\email{caidala@umich.edu}
%\thanks{The first author was supported in part by NSF Grant \#000000.}

\author{Gabriele Carcassi}
\address{Department of Physics; University of Michigan; Ann Arbor, MI 48109}
\email{carcassi@umich.edu}

\author{Mark J. Greenfield}
\address{Department of Mathematics; University of Michigan; Ann Arbor, MI 48109}
\email{markjg@umich.edu}

%    General info
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subjclass[2010]{54H99, 00A79}
%                                                                                                                           %
%         Please use the current 2010 Mathematics Subject Classification:             %
%         http://www.ams.org/mathscinet/msc/                                                        %
%         http://www.zentralblatt-math.org/msc/en/                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\keywords{topological spaces, scientific foundations, function space}
\thanks {Funding for this work was provided in part by the MCubed program of the University of Michigan.}

@@

\maketitle

\section{\bf Introduction}

@@

\section{\bf Experimental observations}

@@

\section{\bf Algebra of experimental observations}

@@

\section{\bf Experimental domain}

@@

\section{\bf Experimental distinguishability}

@@

\section{\bf Experimental relationships}

@@

\section{\bf Distinguishability of experimental relationships}

@@

\section{\bf Conclusion}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{p{0.20\textwidth} p{0.7\textwidth}}
		Math/Topology & Science/Physics \\ 
		\hline 
		Hausdorff, 2nd-countable space & Space of experimentally distinguishable elements, whose points are the possible values and whose open sets represent the experimentally attainable levels of precision. \\
		Open set & Verifiable set. We can verify experimentally that an element is within the set.  \\ 
		Closed set & Refutable set. We can verify experimentally that an element is not in the set. \\ 
		Basis & A collection of verifiable sets that can be used to distinguish an element\\
		Continuous \newline function &  An experimental relationship between two sets of experimentally distinguishable elements, which must preserve distinguishability \\
		Homeo-morphism &  A perfect equivalence between spaces of experimentally distinguishable elements. \\
		\\
	\end{tabular} 
	\caption{Topology-to-physics dictionary. This table sums up the relationships established between mathematical and scientific concepts.}
\end{table}

\bibliographystyle{plain}
\begin{thebibliography}{10}

	\smallskip

	\bibitem{wigner} E. Wigner, {\it The unreasonable effectiveness of mathematics in the natural sciences}, Communications on Pure and Applied Mathematics 13 (1) (1960) 1-14. doi:10.1002/cpa.3160130102.

	\smallskip

	\bibitem{rashevsky} N. Rashevsky, {\it Topology and life: In search of general mathematical principles in biology and sociology}, The bulletin of mathematical biophysics 16 (4) (1954) 317-348. doi:10.1007/BF02484495.

	\smallskip

	\bibitem{chichilnisky} G. Chichilnisk, {\it Social choice and the topology of spaces of preferences}. Advances in Mathematics 37 (2) (1980) 165-176. doi:http://dx.doi.org/10.1016/0001-8708(80)90032-8.

	\smallskip

	\bibitem{nakahara} M. Nakahara, {\it Geometry, topology and physics}, CRC Press, 2003.

	\smallskip

	\bibitem{basener} W. F. Basener, eds. {\it Topology and its applications}, John Wiley \& Sons, 2006.

	\smallskip

	\bibitem{mill}  J. S. Mill, {\it A system of logic}, Parker, 1843

	\smallskip

	\bibitem{russell} B. Russell, {\it The problems of philosophy}, Home University Library, 1912.
\end{thebibliography}
